Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-12-27 paper/paper.tex
Changed wording of helping in third paragraph of discussion. It feels an odd word to use here. Hope that the changed language is a bit better.

These viral defects substantially contribute to the heterogeneity observed in prior single-cell studies of influenza~\citep{russell2018extreme, steuerman2018dissection, heldt2015single, sjaastad2018distinct}, including helping determine if a cell triggers an IFN response.
We identified four types of defects in single IFN+ cells that we validated increase IFN induction. 
Two types of defects---absence of NS and mutations to the NS1 protein---presumably impair NS1's well-known ability to antagonize innate-immune pathways~\citep{garcia1998influenza, hale2008multifunctional}.
The third type of defect, amino-acid mutations in the PB1 protein, is consistent with recent work by showing that mutations to the viral polymerase affect generation of mini-viral RNAs that activate the innate-immune sensor RIG-I~\citep{velthuis2018mini}.
Finally, we found an internal deletion in the PB1 gene that enhances IFN induction, consistent with prior work showing that such deletions are immunostimulatory~\citep{baum2010preference, tapia2013defective, boergeling2015evidence, dimmock2015cloned}.
Given the extensive prior work describing such deletions, it is perhaps surprising we did not identify more of them in our single IFN+ cells.
There may be several reasons: we used relatively pure viral stocks~\citep{xue2016propagation} at modest MOI; our experiments preferentially captured cells with higher viral transcriptional load; and most prior studies have used techniques that can detect large deletions but not subtle point mutations.
The relative importance of different types of viral defects also likely varies across infection conditions, viral strains, and cell types---so it remains an open question as to which defects are most relevant for early immune detection of actual viral infections in humans.

>>>>

These viral defects substantially contribute to the heterogeneity observed in prior single-cell studies of influenza~\citep{russell2018extreme, steuerman2018dissection, heldt2015single, sjaastad2018distinct}, including the probability that a cell triggers an IFN response.
We identified four types of defects in single IFN+ cells that we validated increase IFN induction. 
Two types of defects---absence of NS and mutations to the NS1 protein---presumably impair NS1's well-known ability to antagonize innate-immune pathways~\citep{garcia1998influenza, hale2008multifunctional}.
The third type of defect, amino-acid mutations in the PB1 protein, is consistent with recent work by showing that mutations to the viral polymerase affect generation of mini-viral RNAs that activate the innate-immune sensor RIG-I~\citep{velthuis2018mini}.
Finally, we found an internal deletion in the PB1 gene that enhances IFN induction, consistent with prior work showing that such deletions are immunostimulatory~\citep{baum2010preference, tapia2013defective, boergeling2015evidence, dimmock2015cloned}.
Given the extensive prior work describing such deletions, it is perhaps surprising we did not identify more of them in our single IFN+ cells.
There may be several reasons: we used relatively pure viral stocks~\citep{xue2016propagation} at modest MOI; our experiments preferentially captured cells with higher viral transcriptional load; and most prior studies have used techniques that can detect large deletions but not subtle point mutations.
The relative importance of different types of viral defects also likely varies across infection conditions, viral strains, and cell types---so it remains an open question as to which defects are most relevant for early immune detection of actual viral infections in humans.
